Extended Data

### 2021-10-18 doc/manuscript/Dow_Extended_Data.Rmd
Update Dow_Extended_Data.Rmd

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-5"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_AprilMay = "Extended Data Figure 5"
EDF_tree_rings_TMIN = "Extended Data Figure 6"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 7"

>>>>

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-5"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_AprilMay = "Extended Data Figure 5"
EDF_tree_ring_figs= "Extended Data Figure 6-7"
EDF_tree_rings_TMIN = "Extended Data Figure 6"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 7"
